Suffix Trees und Suffix Arrays

### 2012-03-25 paper/paper.tex
Fixed spacing in figure between graphics and caption. Do not use medskip anymore! Added some figures in section Longest common substring.

@@

\begin{figure}[htb]
\centering
\begin{tikzpicture}[
    level 1/.style = {level distance = 10mm, sibling distance = 35mm},
    level 2/.style = {level distance = 10mm, sibling distance = 25mm},
    level 3/.style = {level distance = 10mm, sibling distance = 20mm},
    edge from parent/.style = {->, draw}
    ]
    \node[branch]{}
    child {
        node[branch]{}
        child[child anchor = north] {
            node[subtree]{}
            edge from parent
            node[left, yshift = 0.5mm]{$ad$}
        }
        child[child anchor = north] {
            node[subtree]{}
            edge from parent
            node[right, yshift = 0.5mm]{$gd$}
        }
        edge from parent
        node[above]{$ad$}
    }
    child {
        node[branch]{}
        child[child anchor = north] {
            node[subtree]{}
            edge from parent
            node[left, yshift = 0.5mm]{$a$}
        }
        edge from parent
        node[left]{$cg$}
    }
    child {
        node[branch]{}
        child[child anchor = north] {
            node[subtree]{}
            edge from parent
            node[left, yshift = 0.5mm]{$ga$}
        }
        child[child anchor = north] {
            node[subtree]{}
            edge from parent
            node[right, yshift = 0.5mm]{$ad$}
        }
        edge from parent
        node[above]{$gac$}
    };
\end{tikzpicture}
\medskip
\caption{$\Sigma^+$-Baum für $\Sigma = \{a, \dots, g\}$}
\label{fig:SigmaPlusTree}
\end{figure}

@@

\begin{figure}[htb]
\centering
\begin{tikzpicture}[
    level 1/.style = {level distance = 10mm, sibling distance = 35mm},
    level 2/.style = {level distance = 10mm, sibling distance = 25mm},
    level 3/.style = {level distance = 10mm, sibling distance = 20mm},
    edge from parent/.style = {->, draw}
    ]
    \node[branch] {}
    child[child anchor = north] {
        node[subtree] {}
        edge from parent[dotted]
    }
    child {
        node[branch] {}
        child {
            node (n) [branch] {}
            child[child anchor = north] {
                node[subtree] {}
                edge from parent[dotted]
            }
            child[child anchor = north] {
                node[subtree] {}
                edge from parent[dotted]
            }
            edge from parent
            node[right] {$u$}
        }
        edge from parent
        node[left] {$v$}
    }
    child[child anchor = north] {
        node[subtree] {}
        edge from parent[dotted]
    };
    \node[left = 2mm] at (n) {$\overline{vu}$};
\end{tikzpicture}
\medskip
\caption{Notation zur Knotenbezeichnung}
\label{fig:NotationZurKnotenbezeichnung}
\end{figure}

@@

\begin{figure}[htb]
\centering
\begin{tikzpicture}[
    level 1/.style = {level distance = 10mm, sibling distance = 45mm},
    level 2/.style = {level distance = 10mm, sibling distance = 25mm},
    level 3/.style = {level distance = 10mm, sibling distance = 15mm},
    edge from parent/.style = {->, draw}
    ]
    \node[branch]{}
    child {
        node[branch]{}
        child {
            edge from parent
            node[left]{$cgag$}
        }
        child {
            node[leaf] {}
            edge from parent
            node[right]{$gcgacgag$}
        }
        edge from parent
        node[above]{$a$}
    }
    child[level distance = 16mm] {
        node[branch]{}
        child {
            node[leaf] {}
            edge from parent
            node[left]{$cgag$}
        }
        child {
            node[leaf] {}
            edge from parent
            node[right]{$g$}
        }
        edge from parent
        node[left]{$cga$}
    }
    child {
        node[branch]{}
        child {
            node[branch]{}
            child {
                node[leaf] {}
                edge from parent
                node[left]{$cgag$}
            }
            child {
                node[leaf] {}
                edge from parent
                node[right]{$g$}
            }
            edge from parent
            node[left]{$a$}
        }
        child {
            node[leaf] {}
            edge from parent
            node[right]{$cgacgag$}
        }
        edge from parent
        node[above]{$g$}
    };
\end{tikzpicture}
\medskip
\caption{Suffix Tree für die Zeichenkette $agcgacgag$}
\label{fig:suffixTreeAgcgacgag}
\end{figure}

@@

\begin{figure}[htb]
\centering
\begin{tikzpicture}[
    level 1/.style = {level distance = 10mm, sibling distance = 40mm},
    level 2/.style = {level distance = 10mm, sibling distance = 30mm},
    level 3/.style = {level distance = 10mm, sibling distance = 20mm},
    edge from parent/.style = {->, draw}
    ]
    { [xshift = 0cm, yshift = 0cm]
        \node {}
        child {
            node[branch] (s1) {}
            child[child anchor = north] {
                node[subtree]{}
                edge from parent[dotted]
            }
            child {
                node[branch] (w1) {}
                child {
                    node[branch] (v1) {}
                    edge from parent
                    node[left]{$u'$}
                }
                edge from parent[solid]
                node[left]{$u$}
            }
            child[child anchor = north] {
                node[subtree]{}
                edge from parent[dotted]
            }
            edge from parent[dotted]
        };
    }
    \node[subtree] at (v1.center) {};
    \node[yshift = 2mm, xshift = 3mm] at (s1.center) {$\overline{s}$};
    \node[right] at (w1.east) {$\overline{w}$};
    \node[right] at (v1.center) {$\overline{v}$};
    { [xshift = 4cm, yshift = {-1cm}]
        \node{$\overset{\overline{w}}{\implies}$};
    }
    { [xshift = 8cm, yshift = 0cm]
        \node{}
        child {
            node[branch] (s2) {}
            child[child anchor = north] {
                node[subtree]{}
                edge from parent[dotted]
            }
            child[level distance = 12mm] {
                node[branch] (v2) {}
                edge from parent[solid]
                node[left]{$uu'$}
            }
            child[child anchor = north] {
                node[subtree]{}
                edge from parent[dotted]
            }
            edge from parent[dotted]
        };
    }
    \node[subtree] at (v2.center) {};
    \node[yshift = 2mm, xshift = 3mm] at (s2.center) {$\overline{s}$};
    \node[right] at (v2.center) {$\overline{v}$};
\end{tikzpicture}
\medskip
\caption{Kantenverschmelzung}
\label{fig:Kantenverschmelzung}
\end{figure}

@@

\medskip

@@

\begin{figure}[htb]
\centering
\begin{tikzpicture}[
    level 1/.style = {level distance = 12mm, sibling distance = 45mm},
    level 2/.style = {level distance = 12mm, sibling distance = 25mm},
    edge from parent/.style = {->, draw}
    ]
    \node[branch]{}
    child {
        node[branch]{}
        child {
            edge from parent
            node[left]{$gcg\$$}
        }
        child {
            edge from parent
            node[right]{$cg\#$}
        }
        edge from parent
        node[above]{$a$}
    }
    child {
        node[branch]{}
        child {
            edge from parent
            node[left]{$\$$}
        }
        child {
            edge from parent
            node[right]{$\#$}
        }
        edge from parent
        node[left]{$cg$}
    }
    child {
        node[branch]{}
        child {
            edge from parent
            node[left]{$cg\$$}
        }
        child {
            edge from parent
            node[left]{$\$$}
        }
        child {
            edge from parent
            node[right]{$\#$}
        }
        edge from parent
        node[above]{$g$}
    };
\end{tikzpicture}
\medskip
\caption{$GST$ für $D = \{agcg, acg\}$ und $T = \{\$, \#\}$}
\label{fig:GSTAgcgAcg}
\end{figure}

@@

\begin{table}
\centering
\begin{tabular}{l}
    \toprule
    All-pairs suffix-prefix matching      \\
    Construction of DAWGs                 \\
    Exact set matching                    \\
    Exact string matching                 \\
    k-mismatch                            \\
    \textbf{Longest common substring}     \\
    Matching statistics                   \\
    Maximal repeated pairs                \\
    Maximal repeats                       \\
    Supermaximal repeats                  \\
    Ziv–Lempel decomposition              \\
    ...                                   \\
    \bottomrule
\end{tabular}
\caption{Anwendungsgebiete für Suffix Trees}
\label{tab:AnwendungsgebieteFuerSuffixTrees}
\end{table}

@@

@@

% [h]: here, [t]: top, [b]: bottom
\begin{figure}[h]
\centering
\begin{tikzpicture}[
    level 1/.style = {level distance = 7mm, sibling distance = 30mm},
    level 2/.style = {level distance = 7mm, sibling distance = 15mm},
    level 3/.style = {level distance = 7mm, sibling distance = 10mm},
    edge from parent/.style = {->, draw}
    ]
    { [yshift = 0cm]
        \node[branch]{}
        child {
            node[ghostbranch] (u) {}
            edge from parent
            node[above]{$a$}
        }
        child[level distance = 8mm] {
            node[ghostbranch] (v) {}
            edge from parent
            node[left]{$cga$}
        }
        child {
            node[ghostbranch] (w) {}
            edge from parent
            node[above]{$g$}
        };
        \node[align = left, anchor = north, yshift = {-1mm}] at (u.center) {$gcgacgag$ \\ $cgag$ \\ $g$};
        \node[align = left, anchor = north, yshift = {-1mm}] at (v.center) {$cgag$ \\ $g$};
        \node[align = left, anchor = north, yshift = {-1mm}] at (w.center) {$cgacgag$ \\ $acgag$ \\ $ag$};
    }
    { [yshift = -3cm]
        \node[branch]{}
        child {
            node[branch]{}
            child {
                edge from parent
                node[left]{$cgag$}
            }
            child {
                edge from parent
                node[right]{$gcgacgag$}
            }
            edge from parent
            node[above]{$a$}
        }
        child[level distance = 16mm] {
            node[branch]{}
            child {
                edge from parent
                node[left]{$cgag$}
            }
            child {
                edge from parent
                node[right]{$g$}
            }
            edge from parent
            node[left]{$cga$}
        }
        child {
            node[branch]{}
            child {
                node[branch]{}
                child {
                    edge from parent
                    node[left]{$cgag$}
                }
                child {
                    edge from parent
                    node[right]{$g$}
                }
                edge from parent
                node[left]{$a$}
            }
            child {
                edge from parent
                node[right]{$cgacgag$}
            }
            edge from parent
            node[above]{$g$}
        };
    }
    { [yshift = -6.5cm]
        \node[branch]{}
        child {
            node[branch]{}
            child {
                edge from parent
                node[left]{$cgag$}
            }
            child {
                edge from parent
                node[right]{$gcgacgag$}
            }
            edge from parent
            node[above]{$a$}
        }
        child[level distance = 16mm] {
            node[branch]{}
            child {
                edge from parent
                node[left]{$cgag$}
            }
            child {
                edge from parent
                node[right]{$g$}
            }
            edge from parent
            node[left]{$cga$}
        }
        child {
            node[branch]{}
            child {
                node[branch]{}
                child {
                    edge from parent
                    node[left]{$cgag$}
                }
                child {
                    edge from parent
                    node[right]{$g$}
                }
                edge from parent
                node[left]{$a$}
            }
            child {
                edge from parent
                node[right]{$cgacgag$}
            }
            edge from parent
            node[above]{$g$}
        };
    }
\end{tikzpicture}
\medskip
\caption{cst-Konstruktion für $t$ = $agcgacgag$}
\label{fig:cstKonstruktion}
\end{figure}

>>>>

%--Figure-Konfiguartion------------------------------------------------------

\setlength{\abovecaptionskip}{5mm}

@@

\begin{figure}[htb]
\centering
\begin{tikzpicture}[
    level 1/.style = {level distance = 10mm, sibling distance = 35mm},
    level 2/.style = {level distance = 10mm, sibling distance = 25mm},
    level 3/.style = {level distance = 10mm, sibling distance = 20mm},
    edge from parent/.style = {->, draw}
    ]
    \node[branch]{}
    child {
        node[branch]{}
        child[child anchor = north] {
            node[subtree]{}
            edge from parent
            node[left, yshift = 0.5mm]{$ad$}
        }
        child[child anchor = north] {
            node[subtree]{}
            edge from parent
            node[right, yshift = 0.5mm]{$gd$}
        }
        edge from parent
        node[above]{$ad$}
    }
    child {
        node[branch]{}
        child[child anchor = north] {
            node[subtree]{}
            edge from parent
            node[left, yshift = 0.5mm]{$a$}
        }
        edge from parent
        node[left]{$cg$}
    }
    child {
        node[branch]{}
        child[child anchor = north] {
            node[subtree]{}
            edge from parent
            node[left, yshift = 0.5mm]{$ga$}
        }
        child[child anchor = north] {
            node[subtree]{}
            edge from parent
            node[right, yshift = 0.5mm]{$ad$}
        }
        edge from parent
        node[above]{$gac$}
    };
\end{tikzpicture}
\caption{$\Sigma^+$-Baum für $\Sigma = \{a, \dots, g\}$}
\label{fig:SigmaPlusTree}
\end{figure}

@@

\begin{figure}[htb]
\centering
\begin{tikzpicture}[
    level 1/.style = {level distance = 10mm, sibling distance = 35mm},
    level 2/.style = {level distance = 10mm, sibling distance = 25mm},
    level 3/.style = {level distance = 10mm, sibling distance = 20mm},
    edge from parent/.style = {->, draw}
    ]
    \node[branch] {}
    child[child anchor = north] {
        node[subtree] {}
        edge from parent[dotted]
    }
    child {
        node[branch] {}
        child {
            node (n) [branch] {}
            child[child anchor = north] {
                node[subtree] {}
                edge from parent[dotted]
            }
            child[child anchor = north] {
                node[subtree] {}
                edge from parent[dotted]
            }
            edge from parent
            node[right] {$u$}
        }
        edge from parent
        node[left] {$v$}
    }
    child[child anchor = north] {
        node[subtree] {}
        edge from parent[dotted]
    };
    \node[left = 2mm] at (n) {$\overline{vu}$};
\end{tikzpicture}
\caption{Notation zur Knotenbezeichnung}
\label{fig:NotationZurKnotenbezeichnung}
\end{figure}

@@

\begin{figure}[htb]
\centering
\begin{tikzpicture}[
    level 1/.style = {level distance = 10mm, sibling distance = 45mm},
    level 2/.style = {level distance = 10mm, sibling distance = 25mm},
    level 3/.style = {level distance = 10mm, sibling distance = 15mm},
    edge from parent/.style = {->, draw}
    ]
    \node[branch]{}
    child {
        node[branch]{}
        child {
            edge from parent
            node[left]{$cgag$}
        }
        child {
            node[leaf] {}
            edge from parent
            node[right]{$gcgacgag$}
        }
        edge from parent
        node[above]{$a$}
    }
    child[level distance = 16mm] {
        node[branch]{}
        child {
            node[leaf] {}
            edge from parent
            node[left]{$cgag$}
        }
        child {
            node[leaf] {}
            edge from parent
            node[right]{$g$}
        }
        edge from parent
        node[left]{$cga$}
    }
    child {
        node[branch]{}
        child {
            node[branch]{}
            child {
                node[leaf] {}
                edge from parent
                node[left]{$cgag$}
            }
            child {
                node[leaf] {}
                edge from parent
                node[right]{$g$}
            }
            edge from parent
            node[left]{$a$}
        }
        child {
            node[leaf] {}
            edge from parent
            node[right]{$cgacgag$}
        }
        edge from parent
        node[above]{$g$}
    };
\end{tikzpicture}
\caption{Suffix Tree für die Zeichenkette $agcgacgag$}
\label{fig:suffixTreeAgcgacgag}
\end{figure}

@@

\begin{figure}[htb]
\centering
\begin{tikzpicture}[
    level 1/.style = {level distance = 10mm, sibling distance = 40mm},
    level 2/.style = {level distance = 10mm, sibling distance = 30mm},
    level 3/.style = {level distance = 10mm, sibling distance = 20mm},
    edge from parent/.style = {->, draw}
    ]
    { [xshift = 0cm, yshift = 0cm]
        \node {}
        child {
            node[branch] (s1) {}
            child[child anchor = north] {
                node[subtree]{}
                edge from parent[dotted]
            }
            child {
                node[branch] (w1) {}
                child {
                    node[branch] (v1) {}
                    edge from parent
                    node[left]{$u'$}
                }
                edge from parent[solid]
                node[left]{$u$}
            }
            child[child anchor = north] {
                node[subtree]{}
                edge from parent[dotted]
            }
            edge from parent[dotted]
        };
    }
    \node[subtree] at (v1.center) {};
    \node[yshift = 2mm, xshift = 3mm] at (s1.center) {$\overline{s}$};
    \node[right] at (w1.east) {$\overline{w}$};
    \node[right] at (v1.center) {$\overline{v}$};
    { [xshift = 4cm, yshift = {-1cm}]
        \node{$\overset{\overline{w}}{\implies}$};
    }
    { [xshift = 8cm, yshift = 0cm]
        \node{}
        child {
            node[branch] (s2) {}
            child[child anchor = north] {
                node[subtree]{}
                edge from parent[dotted]
            }
            child[level distance = 12mm] {
                node[branch] (v2) {}
                edge from parent[solid]
                node[left]{$uu'$}
            }
            child[child anchor = north] {
                node[subtree]{}
                edge from parent[dotted]
            }
            edge from parent[dotted]
        };
    }
    \node[subtree] at (v2.center) {};
    \node[yshift = 2mm, xshift = 3mm] at (s2.center) {$\overline{s}$};
    \node[right] at (v2.center) {$\overline{v}$};
\end{tikzpicture}
\caption{Kantenverschmelzung}
\label{fig:Kantenverschmelzung}
\end{figure}

@@

@@

\begin{figure}[htb]
\centering
\begin{tikzpicture}[
    level 1/.style = {level distance = 12mm, sibling distance = 45mm},
    level 2/.style = {level distance = 12mm, sibling distance = 25mm},
    edge from parent/.style = {->, draw}
    ]
    \node[branch]{}
    child {
        node[branch]{}
        child {
            edge from parent
            node[left]{$gcg\$$}
        }
        child {
            edge from parent
            node[right]{$cg\#$}
        }
        edge from parent
        node[above]{$a$}
    }
    child {
        node[branch]{}
        child {
            edge from parent
            node[left]{$\$$}
        }
        child {
            edge from parent
            node[right]{$\#$}
        }
        edge from parent
        node[left]{$cg$}
    }
    child {
        node[branch]{}
        child {
            edge from parent
            node[left]{$cg\$$}
        }
        child {
            edge from parent
            node[left]{$\$$}
        }
        child {
            edge from parent
            node[right]{$\#$}
        }
        edge from parent
        node[above]{$g$}
    };
\end{tikzpicture}
\caption{$GST$ für $D = \{agcg, acg\}$ und $T = \{\$, \#\}$}
\label{fig:GSTAgcgAcg}
\end{figure}

@@

\begin{table}
\centering
\begin{tabular}{l}
    \toprule
    All-pairs suffix-prefix matching      \\
    Construction of DAWGs                 \\
    Exact set matching                    \\
    Exact string matching                 \\
    k-mismatch                            \\
    Longest common substring              \\
    Matching statistics                   \\
    Maximal repeated pairs                \\
    Maximal repeats                       \\
    Supermaximal repeats                  \\
    Ziv–Lempel decomposition              \\
    ...                                   \\
    \bottomrule
\end{tabular}
\caption{Anwendungsgebiete für Suffix Trees}
\label{tab:AnwendungsgebieteFuerSuffixTrees}
\end{table}

@@

\begin{figure}
\centering
\begin{tikzpicture}[
    level 1/.style = {level distance = 10mm, sibling distance = 60mm},
    level 2/.style = {level distance = 10mm, sibling distance = 30mm},
    level 3/.style = {level distance = 10mm, sibling distance = 20mm},
    edge from parent/.style = {->, draw}
    ]
    \node[branch]{}
    child {
        node[branch]{}
        child {
            node[branch] (w1) {}
            child {
                edge from parent
                node[left]{$a\$$}
            }
            child {
                edge from parent
                node[right, xshift = 1mm]{$ga\#$}
            }
            edge from parent
            node[left]{$g$}
        }
        child {
            edge from parent
            node[right, xshift = 1mm]{$\$, \#$}
        }
        edge from parent
        node[above]{$a$}
    }
    child {
        node[branch]{}
        child {
            node[branch] (w2) {}
            child {
                edge from parent
                node[left]{$ga\$$}
            }
            child {
                edge from parent
                node[right]{$\$, \#$}
            }
            edge from parent
            node[left]{$a$}
        }
        child {
            edge from parent
            node[right, xshift = 2mm]{$ga\#$}
        }
        edge from parent
        node[above]{$g$}
    };
    \node[yshift = 3mm, xshift = -7mm] at (w1.center) {$\overline{w}$} edge [dotted] (w1);
    \node[yshift = 3mm, xshift = -7mm] at (w2.center) {$\overline{w}$} edge [dotted] (w2);
\end{tikzpicture}
\caption{Längstes gemeinsames Teilwort $w$}
\label{fig:LaengstesGemeinsamesTeilwortW}
\end{figure}

\begin{figure}
\centering
\begin{tikzpicture}[
    level 1/.style = {level distance = 10mm, sibling distance = 60mm},
    level 2/.style = {level distance = 10mm, sibling distance = 30mm},
    level 3/.style = {level distance = 10mm, sibling distance = 20mm},
    edge from parent/.style = {->, draw}
    ]
    \node[branch] (b1) {}
    child {
        node[branch] (b2) {}
        child {
            node[branch] (b3) {}
            child {
                node[leaf] (l1) {}
                edge from parent
                node[left]{$a\$$}
            }
            child {
                node[leaf] (l2) {}
                edge from parent
                node[right, xshift = 1mm]{$ga\#$}
            }
            edge from parent
            node[left]{$g$}
        }
        child {
            node[leaf] (l3) {}
            edge from parent
            node[right, xshift = 1mm]{$\$, \#$}
        }
        edge from parent
        node[above]{$a$}
    }
    child {
        node[branch] (b4) {}
        child {
            node[branch] (b5) {}
            child {
                node[leaf] (l4) {}
                edge from parent
                node[left]{$ga\$$}
            }
            child {
                node[leaf] (l5) {}
                edge from parent
                node[right]{$\$, \#$}
            }
            edge from parent
            node[left]{$a$}
        }
        child {
            node[leaf] (l6) {}
            edge from parent
            node[right, xshift = 2mm]{$ga\#$}
        }
        edge from parent
        node[above]{$g$}
    };
    \node[yshift = 8mm] at (b1) {$(1, 1)$} edge [dotted] (b1);
    \node[yshift = 3mm, xshift = -10mm] at (b2) {$(1, 1)$} edge [dotted] (b2);
    \node[yshift = 3mm, xshift = -10mm] at (b3) {$(1, 1)$} edge [dotted] (b3);
    \node[yshift = 3mm, xshift = 10mm] at (b4) {$(1, 1)$} edge [dotted] (b4);
    \node[yshift = 3mm, xshift = -10mm] at (b5) {$(1, 1)$} edge [dotted] (b5);
    \node[yshift = -8mm] at (l1) {$(1, 0)$} edge [dotted] (l1);
    \node[yshift = -8mm] at (l2) {$0, 1)$} edge [dotted] (l2);
    \node[yshift = -18mm] at (l3) {$(1, 1)$} edge [dotted] (l3);
    \node[yshift = -8mm] at (l4) {$(1, 0)$} edge [dotted] (l4);
    \node[yshift = -8mm] at (l5) {$(1, 1)$} edge [dotted] (l5);
    \node[yshift = -18mm] at (l6) {$(0, 1)$} edge [dotted] (l6);
\end{tikzpicture}
\caption{Zuordnung der Bitvektoren}
\label{ZuordnungDerBitvektoren}
\end{figure}

@@

% [h]: here, [t]: top, [b]: bottom
\begin{figure}[h]
\centering
\begin{tikzpicture}[
    level 1/.style = {level distance = 7mm, sibling distance = 30mm},
    level 2/.style = {level distance = 7mm, sibling distance = 15mm},
    level 3/.style = {level distance = 7mm, sibling distance = 10mm},
    edge from parent/.style = {->, draw}
    ]
    { [yshift = 0cm]
        \node[branch]{}
        child {
            node[ghostbranch] (u) {}
            edge from parent
            node[above]{$a$}
        }
        child[level distance = 8mm] {
            node[ghostbranch] (v) {}
            edge from parent
            node[left]{$cga$}
        }
        child {
            node[ghostbranch] (w) {}
            edge from parent
            node[above]{$g$}
        };
        \node[align = left, anchor = north, yshift = {-1mm}] at (u.center) {$gcgacgag$ \\ $cgag$ \\ $g$};
        \node[align = left, anchor = north, yshift = {-1mm}] at (v.center) {$cgag$ \\ $g$};
        \node[align = left, anchor = north, yshift = {-1mm}] at (w.center) {$cgacgag$ \\ $acgag$ \\ $ag$};
    }
    { [yshift = -3cm]
        \node[branch]{}
        child {
            node[branch]{}
            child {
                edge from parent
                node[left]{$cgag$}
            }
            child {
                edge from parent
                node[right]{$gcgacgag$}
            }
            edge from parent
            node[above]{$a$}
        }
        child[level distance = 16mm] {
            node[branch]{}
            child {
                edge from parent
                node[left]{$cgag$}
            }
            child {
                edge from parent
                node[right]{$g$}
            }
            edge from parent
            node[left]{$cga$}
        }
        child {
            node[branch]{}
            child {
                node[branch]{}
                child {
                    edge from parent
                    node[left]{$cgag$}
                }
                child {
                    edge from parent
                    node[right]{$g$}
                }
                edge from parent
                node[left]{$a$}
            }
            child {
                edge from parent
                node[right]{$cgacgag$}
            }
            edge from parent
            node[above]{$g$}
        };
    }
    { [yshift = -6.5cm]
        \node[branch]{}
        child {
            node[branch]{}
            child {
                edge from parent
                node[left]{$cgag$}
            }
            child {
                edge from parent
                node[right]{$gcgacgag$}
            }
            edge from parent
            node[above]{$a$}
        }
        child[level distance = 16mm] {
            node[branch]{}
            child {
                edge from parent
                node[left]{$cgag$}
            }
            child {
                edge from parent
                node[right]{$g$}
            }
            edge from parent
            node[left]{$cga$}
        }
        child {
            node[branch]{}
            child {
                node[branch]{}
                child {
                    edge from parent
                    node[left]{$cgag$}
                }
                child {
                    edge from parent
                    node[right]{$g$}
                }
                edge from parent
                node[left]{$a$}
            }
            child {
                edge from parent
                node[right]{$cgacgag$}
            }
            edge from parent
            node[above]{$g$}
        };
    }
\end{tikzpicture}
\caption{cst-Konstruktion für $t$ = $agcgacgag$}
\label{fig:cstKonstruktion}
\end{figure}
